A Simplified Plackett-Luce Likelihood Function for Rank Orders

### 2025-01-22 inst/hankin-AustrianJournalofStatistics.tex
typo

Here a new simplification of the Plackett--Luce likelihood functions
for order statistics is proposed.  We consider a field of $n$ entities
that are ordered in some way [the preferred example is competitors in
  a running race, ordered by time of crossing the finishing line].
One entity is of particular interest to us: the ``focal entity'', or
focal competitor.  We assign Plackett--Luce strength $a$ to the focal
competitor and $b$ to all others; we require $a+b=1$.  The associated
inference problem has a wide range of applications and I present some
analysis of datasets drawn from the fields of Olympic athletics,
education, and Formula~1 motor racing.

>>>>

Here a new simplification of the Plackett--Luce likelihood functions
for order statistics is proposed.  We consider a field of $n$ entities
that are ordered in some way [the preferred example is competitors in
  a running race, ordered by time of crossing the finishing line].
One entity is of particular interest to us: the ``focal entity'', or
focal competitor.  We assign Plackett--Luce strength $a$ to the focal
competitor and $b$ to all others; we require $a+b=1$.  The associated
inference problem has a wide range of applications and I present some
analysis of datasets drawn from the fields of amateur athletics,
education, and Formula~1 motor racing.
